### 2020-01-02 docs/thesis-project/article.tex
Update article.tex

Following the suggestions of Cloudcast authors, H. Kavalionak \textit{et al.}, developed a decentralized algorithm\cite{marriage_of_convinience} that aims to do replica management in cloud-based, peer-assisted applications. Because the proposed work has no running title, we shall refer to it as ARM. The goal of the ARM is to maintain an appropriate replication level, despite churn, such that, at all times, at least one replica is available and ensuring that replicas survive failures. Furthermore, the proposal acknowledges that replicas should be synchronized, i.e., the system should support session guarantees. The main difference between ARM and Cloudcast is that in the latter, the cloud server stores all updates in an always-on passive cloud server helping with information dissemination when needed, whereas, in the former, the cloud does not participate in the system at all, unless conditions are extreme. Cloudcast monetary cost reductions are thus, primarily associated with limiting access to the cloud server, and ARM effectively reduces those costs further by performing timely switches between Cloudcast and regular Cyclon protocols, depending on the size of the network. To estimate the network size without centralization or broadcasting that would ultimately lead to either bottlenecks or overhead, ARM leverages a gossip aggregation method that allows each peer to infer the approximate size of the network autonomously, at the end of each epoch. Estimation accuracy is dependent only on the size of the epoch. Likewise, the execution cost depends on the length of the epochs and the network churn rate, but not on the number of peers in the system, which means that ARM keeps the scale-free properties of the unstructured overlays that used in Cloudcast. The peers randomly organize themselves according to the Cyclon peer-sampling protocol, but depending on the results of the aggregation, the passive cloud-server used in Cloudcast is removed or kept in the overlay. In ARM, each data object to be replicated as its \textit{replica-overlay} on top of the regular unstructured overlay, which facilitates synchronization and cloud-usage decisions. The ARM algorithm is designed to consider four replica-overlay states, separated by three size thresholds: \textit{Critical (C)}, \textit{Sufficient (S)} and \textit{Redundant (S)}. \textit{C} depends on the chosen redundancy method, i.e., file-level \textit{vs.} block-level replication and is the sum of the minimum number of replicas required for data recovery plus the number of peers that will leave during the cloud backup replication phase. \textit{S} depends on the churn-rate and is the sum of \textit{C} plus the number of peers expected between two successive recovery phases. Finally, \textit{R} is a system parameter dependent also on the chosen redundancy method and is application requirements specific.  The aggregation method mentioned earlier is the foundation \textit{monitoring phase}, which consists of a fixed number of gossip and idle rounds, allowing a peer to infer the \textit{expected size (N\textsubscript{e})} of the replica-overlay and decide if he should add or remove the cloud or peers to the replica-overlay as well as the protocol he uses, based on Algorithm \ref{alg:makedecision}. After each monitoring phase, each peer calculates how long it should wait before executing the \textit{monitoring phase} again. That time depends mostly on \textit{N\textsubscript{e}}, e.g., if the state is below the critical threshold, the monitoring phase will initiate earlier than if it is above the redundant threshold, allowing the system to respond to overlay changes promptly and to keep the overlay size in a range that minimizes overhead but ensures that data does not become unavailable. The authors do not specify how much savings the system was capable of achieving using ARM; however, we can assume it is a substantial value; In Fig. \ref{fig:arm_results}, the plot on top displays the number of peers in the underlying network as a function of time, and the bottom plot shows the in-degree to the cloud server as a function of time, comparing Cloudcast and ARM (labeled as "our protocol").

@@

\newpage\section{Data Redundancy and File Survivability}\label{sec:dataredundancy}
In distributed storage systems, not losing files is of the utmost importance. Particularly, since peer availability in P2P networks is ever-changing and not guaranteed, the availability and even durability of a file may be endangered. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. For clarity, an available file is durable, but the other way is not necessarily correct. Distributed systems as a whole, usually ensure durability by employing file-level or block-level \textbf{\textit{replication}}; alternatively, some systems adopt \textbf{\textit{erasure coding}} techniques (\textit{coding} for short) or a mixture of both approaches. Replication has the advantage of having a more straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on the survivability of files in P2P networks, using swarm guidance, where resources may be limited, we care only about coding in the survey that follows, briefly mentioning some of the raised concerns and inherent disadvantages of this technique.

>>>>

Following Cloudcast suggestions, H. Kavalionak \textit{et al.}, developed a solution\cite{marriage_of_convinience} that we shall refer to as ARM, with the goal of maintaining an appropriate data replication level, despite churn and, in such a way that peers sharing the same data object are synchronized, i.e., the system should support session guarantees. The main difference between ARM and Cloudcast is that in the latter, the cloud server stores all updates in an always-on passive cloud server that helps with information dissemination, whereas, in the former, the cloud does not participate in the system at all, unless conditions are extreme. Cloudcast monetary cost reductions result from limiting cloud accesses, and ARM effectively reduces those costs further by performing timely switches between Cloudcast and regular Cyclon-based protocols, depending on the size of the network. To estimate that size without centralized or broadcast solutions that could, respectively, lead to bottlenecks or bandwidth waste, ARM periodically runs a monitoring phase whose accuracy dependents only on its duration and whose execution cost depends on the network churn rate, but not on the number of peers in the system. Peer neighboring relations are built naturally from Cyclon peer-sampling, but depending on the results of the aggregation, the cloud server is either removed or kept in the overlay. The decision to add or remove the cloud depends on the following threshold: \textit{Critical (C)} equals the minimum number of replicas required for data recovery plus the number of peer faults the system must support during cloud replication. \textit{Sufficient (S)} depends on the churn-rate and equals \textit{C} plus the number of peers expected between two successive recovery phases. Finally, \textit{Redundant (S)} is an application-specific system parameter. The monitoring phase thus, consists of a fixed number of gossip and idle rounds, allowing a peer to infer the \textit{expected size (N\textsubscript{e})} of the overlay based on Algorithm \ref{alg:makedecision}. After each monitoring phase, peers independently calculate how long they should wait before re-executing the phase. That time depends mostly on \textit{N\textsubscript{e}}, e.g., if the state is below the critical threshold, the monitoring phase will initiate earlier than if it is above the redundant threshold, allowing the system to respond to overlay changes promptly and to keep the overlay size in a range that minimizes overhead but ensures that data does not become unavailable. The authors do not specify how much savings the system was capable of achieving using ARM; however, we can assume it is a substantial value; In Fig. \ref{fig:arm_results}, the plot on top displays the number of peers in the underlying network as a function of time, and the bottom plot shows the in-degree to the cloud server as a function of time, comparing Cloudcast and ARM\footnote{ARM is labeled as "our protocol"}.

@@

\section{Data Redundancy and File Survivability}\label{sec:dataredundancy}
In distributed storage systems, not losing files is of the utmost importance. Particularly, since peer availability in P2P networks is ever-changing and not guaranteed, the availability and even durability of a file may be endangered. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. For clarity, an available file is durable, but the other way is not necessarily correct. Distributed systems as a whole, usually ensure durability by employing file-level or block-level \textbf{\textit{replication}}; alternatively, some systems adopt \textbf{\textit{erasure coding}} techniques (\textit{coding} for short) or a mixture of both approaches. Replication has the advantage of having a more straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on the survivability of files in P2P networks, using swarm guidance, where resources may be limited, we care only about coding in the survey that follows, briefly mentioning some of the raised concerns and inherent disadvantages of this technique.
